Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-15 WRITEUP/ms.tex
ss number and galaxy age

From the dispersion relation, a parameter $Q$ can be derived such that $Q < 1$ when instability occurs, that reproduces this inequality to order unity.
For a collisionless fluid---such as an ensemble of stars--- this parameter is \citep{Toomre64a}
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}
The equivalent parameter for a collisional gas was derived by
%mm [corrected from Toomre64a to Goldreich65a (not Goldreich65b, which is about spiral arm formation)]
    \citep{Goldreich65a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). 
%mm  In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
     A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion
$v_{\rm circ}/\sigma_{\rm disk}$
%mm , i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} \MM{see above} ratio 
\citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis

In our stability analysis, we account for the combined effect of gas and stars 
%mm 
     \citep[derived exactly by][]{Rafikov01}, 
and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
maintain 
stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}.
%
On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
$Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2

@@

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as winds from OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
\DL{AP: please elaborate non-thermal pressure here..}
Photoionization from local sources is neglected in this simulation
\citep[see][for its effect]{pallottini:2019,decataldo:2019}. 
%mm \AP{modified accordingly}

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
accretes mass from the IGM mainly via three filaments of length
$\simeq$\,100\,kpc. \flower has a stellar mass of
$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of
%mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
   30\,--\,80\,\Msun\,yr\pmOne. 
%mm \MM{What is its gas fraction?  I ask because its molecular gas
%mass is minuscule, particularly for such a high SFR: this is a
%depletion time of only 0.5 Myr, while modern galaxies usually have
%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
%flickering and depends on which radius we are considering, as the
%galaxy is actively accreating material and merging; depletion time
%are low, see the ssfr note added considering that $ssfr \propto
%t_{depletion}^{-1}$} 
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
relation observed at high redshift \citep{Jiang2016}, which is higher
than normal local galaxies. The effective stellar radius of \flower
is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
  200}\simeq$\,15\,kpc.

@@

One of the main advantages for studying the dynamical properties of simulated galaies is that we can examine how their properties evolve with time.
%
%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF. Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
%mm [delete para break]
The \SF history\footnote{Note that here the SFR is calculated based on
  the stellar mass formed in the last 4 Myr within 3.5 kpc from the
  galaxy center of mass. The SFR plotted in Figure 2 of
  \citet{Pallottini17b} is a factor of two higher since there the SFR
  accounts for the contribution from massive satellite galaxies within
  the virial radius ($\approx$15\,kpc).} of \flower is shown in
\Fig{SFH}. The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given the stochastic nature of \flower in its star formation history, we mostly focus on
two of its most extreme evolutionary stages in this work (see \Sec{singless}).
The two phases correspond to (a) an intensely accreting phase and
(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
MCC properties are sensitive to these different dynamical
conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced
in the simulation (see \Sec{ncut}).

Throughout this paper, we 
%mm dub as ``satellite galaxies'' the dense gas regions outside the
%main disk of \flower. 
     describe  the dense gas regions outside the main disk of \flower
     as satellite galaxies.
The distinction between clumps and satellites is admittedly somewhat
ambiguous, though, and we consider it only as a working one.

@@

To visually display 
the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.

The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
We also compute the Mach number from turbulent and thermal pressure to determine the importance of 
differential rotation in the derived velocity dispersion: 
\begin{equation}
\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}\,,
\label{eqn:MPress}
\end{equation}
where $P_{\rm NT}$ is non-thermal pressure and $P$ is thermal pressure.

@@

%\begin{figure*}
%% \centering
%\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
%% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
%\caption{
%% Top: 
%Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
%% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
%Definition of the symbol shown are the same as in \Fig{larsons_single}.
%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
%Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
%% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
%\label{fig:alpha21-22}}
%\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from top left to bottom left, followed by top right to bottom right.
Definition of symbols shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
The virial parameter vary over the $\sim$300\,Myr shown here, as \flower\ evolves.
The variation is clearly seen between the pre-starburst through post-starburst phase. 
\label{fig:alphaEvol}}
\end{figure*}
{\bf CHECK if I am plotting the righ alphaVIR snapshots../.}

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
\caption{
Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
% ss20,21,22,27
The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
\label{fig:Mach_stellarRatio}}
\end{figure}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCC structures on small and large
scales via two physical properties: mass and size \citep{Larson81a,
  McKee07a}. This is also known as the constant column density
relation,
\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
  $\Sigma$.  Effectively, Larson's mass-size relation is a single
  point on that relationship, at the constant $\Sigma$ value.  This
  suggests that the mass-size relation is just an artifact of the
  narrow range of column densities observed with $^{12}CO$, as
  suggested among others by \citet{Ballesteros11}.}
since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

@@

\DL{
1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
% 
3) overall lower alphavir in the pre-SB phase in \Fig{alphaEvol}. 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}

@@

>>>>

From the dispersion relation, a parameter $Q$ can be derived such that $Q < 1$ when instability occurs, that reproduces this inequality to order unity.
For a collisionless fluid---such as an ensemble of stars--- this parameter is \citep{Toomre64a}
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}
The equivalent parameter for a collisional gas was derived by
%mm [corrected from Toomre64a to Goldreich65a (not Goldreich65b, which is about spiral arm formation)]
    \citep{Goldreich65a}
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). 
%mm  In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
     A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion
$v_{\rm circ}/\sigma_{\rm disk}$
%mm , i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} \MM{see above} ratio 
\citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis

In our stability analysis, we account for the combined effect of gas and stars 
%mm 
     \citep[derived exactly by][]{Rafikov01}, 
and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
maintain 
stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}.
%
On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
$Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2

@@

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as winds from OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
\DL{AP: please elaborate non-thermal pressure here..}
Photoionization from local sources is neglected in this simulation
\citep[see][for its effect]{pallottini:2019,decataldo:2019}.

The simulation zooms in on a galaxy named after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
accretes mass from the IGM mainly via three filaments of length
$\simeq$\,100\,kpc. \flower has a stellar mass of
$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne. 
%mm \MM{What is its gas fraction?  I ask because its molecular gas
%mass is minuscule, particularly for such a high SFR: this is a
%depletion time of only 0.5 Myr, while modern galaxies usually have
%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
%flickering and depends on which radius we are considering, as the
%galaxy is actively accreating material and merging; depletion time
%are low, see the ssfr note added considering that $ssfr \propto
%t_{depletion}^{-1}$} 
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
relation observed at high redshift \citep{Jiang2016}, which is higher
than normal local galaxies. The effective stellar radius of \flower
is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
  200}\simeq$\,15\,kpc.

@@

One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which
is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
%
%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF. Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
%mm [delete para break]
The \SF history\footnote{Note that here the SFR is calculated based on
  the stellar mass formed in the last 4 Myr within 3.5 kpc from the
  galaxy center of mass. The SFR plotted in Figure 2 of
  \citet{Pallottini17b} is a factor of two higher since there the SFR
  accounts for the contribution from massive satellite galaxies within
  the virial radius ($\approx$15\,kpc).} of \flower is shown in
\Fig{SFH}. The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given the stochastic nature of \flower in its star formation history, we mostly focus on
two of its most extreme evolutionary stages in this work (see \Sec{singless}).
These phases correspond to (a) an intensely accreting phase and
(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
MCC properties are sensitive to these different dynamical
conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages 
traced in the simulation (see \Sec{ncut}). 
In \Sec{rot}, we examine the importance of rotation support in the MCC dynamics and
discuss the implication of this finding in \Sec{rotDiss}.

Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies.
The distinction between clumps and satellites is admittedly somewhat
ambiguous, though, and we consider it only as a working one.

@@

To visually display 
the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
The full velocity dispersion of MCCs is calculated from 
the bulk velocity field $\sigma_{\rm bulk}$, non-thermal velocity dispersion $\sigma_{\rm NT}$, and thermal sound speed $c_s$, following
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + \sigma_{\rm bulk}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
For instance, the bulk is calculated as follows
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
Similarly, the non-thermal velocity dispersion is calculated as follows
\begin{equation}
\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,
\end{equation}
and the thermal sound speed is calculated through
\begin{equation}
%        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
\end{equation}
where $P_{\rm NT, i}$ and $P_i$ are the non-thermal and thermal pressures of cell $i$ in units of [K\,\cc], respectively, $k_B$ is the Boltzmann constant, and 
$M_p$ is the mass of a proton.

The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
We also compute the Mach number from turbulent and thermal pressures following
\begin{equation}
\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}.
\label{eqn:MPress}
\end{equation}
% to track its variation over the evolutionary stages of \flower.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through 
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase. 
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
\label{fig:alphaEvol}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
\caption{
Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
% ss20,21,22,27
The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
\DL{replace w/ non-thermal velocity versus bulk velocity plot to investigate importance of differential rotation in the derived velocity dispersion.}
\label{fig:Mach_stellarRatio}}
\end{figure}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCC structures on small and large
scales via mass and size \citep{Larson81a,
  McKee07a}. Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
which is related to the column density ($N_H$) that is obtainable from extinction maps ($A_V$), the mass-size relation is 
also known as the constant column density relation. 
\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
  $\Sigma$.  Effectively, Larson's mass-size relation is a single
  point on that relationship, at the constant $\Sigma$ value.  This
  suggests that the mass-size relation is just an artifact of the
  narrow range of column densities observed with $^{12}CO$, as
  suggested among others by \citet{Ballesteros11}.}
  \DL{will discuss implication in \Sec{MR}.}
By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we adopt $\mu = 2.5$ as the mean molecular weight.

@@

\DL{
1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) Comment somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower \Fig{alphaEvol}.
% 
3) overall lower alphavir in the pre-SB phase in \Fig{alphaEvol}. 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
4) 
}

@@

\subsection{Importance of Rotation in Molecular Structures Observed To-date} \label{sec:rotDiss}
read paper on angular momentum of clouds in \citep{Jappsen04a}.
